Further Evidence of Modified Spin-down in Sun-like Stars:\\Pile-ups in the Temperature--Period Distribution

### 2022-02-02 src/ms.tex
adding shifted models figure

\begin{figure*}
    \centering 
    \includegraphics[width=0.49\linewidth]{./figures/std-model-cks-shifted.pdf}
    \includegraphics[width=0.49\linewidth]{./figures/wmb-model-cks-shifted.pdf}
    \includegraphics[width=0.49\linewidth]{./figures/std-model-lamost-shifted.pdf}
    \includegraphics[width=0.49\linewidth]{./figures/wmb-model-lamost-shifted.pdf}
    \caption{The \teff-\prot plane for the CKS sample (top panels) and LAMOST sample (bottom panels) in comparison to the standard and WMB models (2-d histograms) presented in \citet{vanSaders2019}. Shown here are stars with \logg~$>$~4.1. Rotation periods for the CKS sample here are sourced from the \citet{David2021} compilation. The black symbol in each panel indicates the position of the Sun.}
    \label{fig:shifted}
\end{figure*}

>>>>

\begin{figure*}
    \centering 
    \includegraphics[width=0.49\linewidth]{./figures/std-model-cks-shifted.pdf}
    \includegraphics[width=0.49\linewidth]{./figures/wmb-model-cks-shifted.pdf}
    \includegraphics[width=0.49\linewidth]{./figures/std-model-lamost-shifted.pdf}
    \includegraphics[width=0.49\linewidth]{./figures/wmb-model-lamost-shifted.pdf}
    \caption{Same as Figure~\ref{fig:models} with constant \teff offsets applied to the data. Shifts of +116~K and +140~K are applied to the CKS and LAMOST \teff, respectively. The CKS \teff shift originates from a least-squares fit of a \rocrit~=~2 curve (with a \teff offset) to the long-period pile-up (as described in \S\ref{subsec:rossby}). The LAMOST shift is derived in a similar fashion, with an additional +34~K offset which represents the systematic offset between CKS and LAMOST (see Appendix~\ref{app:teff}).}
    \label{fig:shifted}
\end{figure*}
